\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/discussion.tex
added short reverse engineering section about points-to problem in discussion

>>>>

Alternatively an analyst may attempt to identify sections of the program or dead 
code that will be used to access the probe array and thereby find the speculative 
gadgets. However, identifying sections of memory that will access the probe 
array is equivalent to the "Must Alias" or "Points-To Problem" which has been 
proven undecidable without significant 
restrictions~\cite{ramalingam1994undecidability,landi1992undecidability}.

%
% Theorem 1. ([7, 10]) Single procedural flow-sensitive points-
% to analysis with dynamic memory and non-scalar variables
% is undecidable.
% Our first result improves the above undecidability result
% to
% Theorem 2. Single procedural flow-sensitive points-to
% analysis with dynamic memory is undecidable, even when
% only scalar variables are allowed.
%
